An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-08 main.tex
Build with bibliography.

% \usepackage[backend=biber, firstinits=false, backref=false, url=true,
%             isbn=true, style=numeric]{biblatex}
% \addbibresource{./tex/bibliography.bib}

@@

The Moran Process \cite{Moran1957} is a model of
evolutionary population dynamics that has been used to gain insights about the
evolutionary stability and fixation of strategies in a number of settings.
Similarly since the first Iterated Prisoner's Dilemma (IPD) tournament described in
\cite{Axelrod1980a}, the Prisoner's dilemma has been used to understand the
evolution of cooperative behaviour in complex systems. Several earlier
works have studied iterated games in the context of the prisoner's dilemma
\cite{Nowak} \cite{Stewart2012}.

This manuscript provides a detailed numerical analysis of \textbf{164}
complex and adaptive strategies for the IPD\@. This is made possible
by the Axelrod library \cite{axelrodproject}, an effort to provide
software for reproducible research for the IPD. The library now contains over 150
parameterized strategies including classics like TitForTat and WinStayLoseShift,
as well as recent variants such as OmegaTFT, zero determinant and other memory one strategies,
strategies based on finite state machines, lookup tables, neural networks,
and other machine learning based strategies, and a collection of novel strategies.
The library can conduct matches, tournaments and population dynamics
with variations including noise and spatial structure.

@@

Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
and highly-praised \cite{Stewart26062012} it was argued that 
generous ZD strategies are robust against invading strategies. However,
in \cite{Lee2015} a strategy using machine learning techniques was
capable of resisting invasion and also able to invade any memory one strategy. 
Recent work \cite{Hilbe2017} has investigated the effect of memory length on 
strategy performance and the emergence of cooperation but this is not done in 
Moran process context and only considers specific cases of memory 2 strategies.
In \cite{Adami2013} it was recognized that many zero determinant strategies do
not fare well against themselves. This is a disadvantage for the Moran process
where the best strategies cooperate well with other players using the same strategy.

@@

% \printbibliography

>>>>

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{./tex/bibliography.bib}

@@

The Moran Process \cite{Moran1957} is a model of
evolutionary population dynamics that has been used to gain insights about the
evolutionary stability and fixation of strategies in a number of settings.
Similarly since the first Iterated Prisoner's Dilemma (IPD) tournament described in
\cite{Axelrod1980a}, the Prisoner's dilemma has been used to understand the
evolution of cooperative behaviour in complex systems. Several earlier
works have studied iterated games in the context of the prisoner's dilemma
\cite{Nowak, Stewart2012}.

This manuscript provides a detailed numerical analysis of \textbf{164} complex
and adaptive strategies for the IPD\@. This is made possible by the Axelrod
library \cite{axelrodproject}, an effort to provide software for reproducible
research for the IPD\@. The library now contains over 150 parameterized
strategies including classics like TitForTat and WinStayLoseShift, as well as
recent variants such as OmegaTFT, zero determinant and other memory one
strategies, strategies based on finite state machines, lookup tables, neural
networks, and other machine learning based strategies, and a collection of novel
strategies. The library can conduct matches, tournaments and population
dynamics with variations including noise and spatial structure.

@@

Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
and highly-praised \cite{Stewart2012} it was argued that
generous ZD strategies are robust against invading strategies. However,
in \cite{Lee2015} a strategy using machine learning techniques was
capable of resisting invasion and also able to invade any memory one strategy.
Recent work \cite{Hilbe2017} has investigated the effect of memory length on
strategy performance and the emergence of cooperation but this is not done in
Moran process context and only considers specific cases of memory 2 strategies.
In \cite{Adami2013} it was recognized that many zero determinant strategies do
not fare well against themselves. This is a disadvantage for the Moran process
where the best strategies cooperate well with other players using the same strategy.

@@

\printbibliography
